Comparing OTU quality across clustering strategies

### 2021-07-23 exploratory/2021/algorithm_diagram.Rmd
Trying to get dist_mat out of Python into R

@@

## do backend in python until the actual plotting step

```{r pseudo_optifit}
reticulate::source_python(here('code', 'py', 'algorithm_diagram.py'))
optifit_iters <- run_optifit() %>% 
  lapply(function(x) {
    return(list(nodes = x[['nodes']] %>% py_to_r(),
                edges = x[['edges']] %>% py_to_r() %>% 
                 mutate(is_loop = from == to)))
    })
```

>>>>

## Pat's OptiClust diagram

@@

## do backend in python until the actual plotting step
```{python optifit}
import code.py.algorithm_diagram
optifit = create_optifit()
iters = optifit.iterate
dists = dist_sets_to_array(optifit.fitmap.dist_mat)
```
```{r pytor}
reticulate::source_python(here('code', 'py', 'algorithm_diagram.py'))
optifit <- create_optifit() 
dist_array <- optifit$fitmap$dists_to_array %>% py_to_r()
optifit_iters <- optifit$iterate %>% 
  lapply(function(x) {
    return(list(nodes = x[['nodes']] %>% py_to_r(),
                edges = x[['edges']] %>% py_to_r() %>% 
                 mutate(is_loop = from == to)))
    })
```
